\projectname: A systematic search for transits in \KT\ data

### 2015-01-28 ms.tex
CDS address
intro text

%
%  RULES OF THE GAME
%
%  * 80 characters
%  * line breaks at the ends of sentences
%  * eqnarrys ONLY
%  * that is all.
%

@@

\newcommand{\project}[1]{\emph{#1}}
\newcommand{\kepler}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\terra}{\project{TERRA}}
\newcommand{\license}{MIT License}
\newcommand{\projectname}{\project{KETU}}

@@

\newcommand{\nyu}{2}
\newcommand{\caltech}{3}
\newcommand{\cfa}{4}
\newcommand{\mpia}{5}
\newcommand{\cds}{6}
\newcommand{\mpis}{7}
\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\nyu},
    Benjamin~T.~Montet\altaffilmark{\caltech,\cfa},
    David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
    Bernhard~Sch\"olkopf\altaffilmark{\mpis},
    Dun~Wang\altaffilmark{\nyu},
    \etal
}
\altaffiltext{1}         {To whom correspondence should be addressed:
                          \url{danfm@nyu.edu}}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\caltech}  {California Institute of Technology, Pasadena, CA,
                          91125, USA}
\altaffiltext{\cfa}      {Harvard-Smithsonian Center for Astrophysics,
                          Cambridge, MA 02138, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cds}      {Center for Data Science,
                          New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems
                          Spemannstrasse 38, 72076 T\"ubingen, Germany}

@@

>>>>

%
%  RULES OF THE GAME
%
%  * 80 characters
%  * line breaks at the ends of sentences
%  * eqnarrys ONLY
%  * ``light curve'' not ``light-curve'' or ``lightcurve''
%  * that is all.
%

@@

\newcommand{\project}[1]{\textsl{#1}} % hogg say
\newcommand{\kepler}{\project{Kepler}}
\newcommand{\KT}{\project{K2}}
\newcommand{\tess}{\project{TESS}}
\newcommand{\terra}{\project{TERRA}}
\newcommand{\license}{MIT License}
\newcommand{\projectname}{\project{KETU}}

@@

\newcommand{\nyu}{2}
\newcommand{\caltech}{3}
\newcommand{\cfa}{4}
\newcommand{\mpia}{5}
\newcommand{\cds}{6}
\newcommand{\mpis}{7}
\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\nyu},
    Benjamin~T.~Montet\altaffilmark{\caltech,\cfa},
    David~W.~Hogg\altaffilmark{\nyu,\mpia,\cds},
    Bernhard~Sch\"olkopf\altaffilmark{\mpis},
    Dun~Wang\altaffilmark{\nyu},
    \etal
}
\altaffiltext{1}         {To whom correspondence should be addressed:
                          \url{danfm@nyu.edu}}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\caltech}  {California Institute of Technology, Pasadena, CA,
                          91125, USA}
\altaffiltext{\cfa}      {Harvard-Smithsonian Center for Astrophysics,
                          Cambridge, MA 02138, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\cds}      {Center for Data Science,
                          New York University,
                          726 Broadway, 7th Floor, New York, NY, 10003, USA}
\altaffiltext{\mpis}     {Max Planck Institute for Intelligent Systems
                          Spemannstrasse 38, 72076 T\"ubingen, Germany}

@@

The \kepler\ Mission (cite something) has been incredibly succesful at
finding periodic transits (eclipses) in the light curves (time-series
photometry) of stars.
Many of its most important discoveries are long-period planets that
make transits with tiny amplitudes and short durations.
The Mission has demonstrated that it is possible to routinely measure
signals in stellar light curves at the part-in-$10^5$ level, at least
for quiet and apparently bright stars.

At this level of precision, many effects come in to play in a stellar
light curve.
Even in a space observatory like the \kepler\ Satellite, there are
hardware and optics variations that affect simple photometric
measurements at a level greater than part-in-$10^5$.
One of the most serious of these is spacecraft pointing:
If the detector flat-field is not known \emph{exquisitely}, then the
tiny changes to the relative illumination of pixels caused by a star's
motion in the focal plane (or caused by motion of the focal-plane
boresight or orientation relative to the celestial sphere) will lead
to changes in the measured or inferred brightness of the star.
That is, good photometry relies on either a near-perfect flat-field
and pointing model, or else data-analysis techniques that are
insensitive to such variations.
In this \paper\ we present an example of the latter---a
data-analysis technique for exoplanet search and characterization that
is insensitive to spacecraft-induced (or, in general,
hardware-induced) trends in the light curves.

The \KT\ Mission (cite something) is a follow-on to the primary
\kepler\ Mission.
The primary mission came to an end with the failure of a critical
reaction wheel, rendering the spacecraft less able to maintain precise
pointing.
Because of the degraded spacecraft orientation systems, the new
\KT\ data will in general exhibit far greater pointing
variations---and far greater pointing-induced variations in
photometry---than the original \kepler\ data.
This makes good data-analysis techniques all the more valuable.

...simultaneous fitting of systematics and transit signals is a way of
searching for (and measuring) exoplanet signals independent of the
systematics, provided that the systematics lie in the domain of the
model.

...we are not the first to search the \KT\ data (cite Crossfield, etc),
and we build on ideas from \kepler\ searches (cite Petigura and
\kepler).

...The future is \tess (cite something); everything we do here is
highly relevant to that important mission!
